The Blessing of FedAvg's Linear Speedup in Federated Learning

### 2020-05-28 source/sec_exp.tex
nesterov sgd linear regression results

\textbf{Partial participations.} We verify the linear speedup in the
partial participation settings, where we set only $50\%$ of devices
are active. As the results shown in Figure~\ref{fig:partial}, the 
FedAve enjoys linear speedup in various settings even with partial
device participation.

@@

>>>>

\textbf{Partial participations.} We verify the linear speedup in the
partial participation settings, where we set $50\%$ of devices
are active. As the results shown in Figure~\ref{fig:partial}, the 
FedAve enjoys linear speedup in various settings even with partial
device participation.

@@

\begin{figure}
\centering
\begin{tabular}{ccc}
 &  & 
\includegraphics[width=0.33\textwidth]{fig/paper-lrnesterovspeedupNodesT-min-linearregressionw8a-epsilon002-reg0.pdf}\\
(a) Strongly convex objective & (b) Convex smooth objective & (c) Linear regression
	\end{tabular}
\caption{The linear speedup convergence of Accelerated FedAvg w.r.t the number of workers. }
\label{fig:nesterov}
\end{figure}
